### 2021-09-08 input/proposal.tex
three phase purge

\begin{theorem}[\label{theo:threephase}\TODO{Three-phase purge}]
  The following three phases are sufficient to eventually purge the
  system from stale control information:
  \begin{inparaenum}[(i)]
  \item propagation of delete notifications,
  \item detection of possibly blocking conditions, and
  \item propagation of possibly deleted but blocked notifications.
  \end{inparaenum}
\end{theorem}

@@

  These exceptions eventually receive and deliver $\alpha_Y$ since
  $\alpha_Y$ is better than $\alpha_X$ through this path, except if
  they already received and deliver the removal notification of $P_Y$
  (such as $c$). These \processes may never receive hence deliver
  $\delta_X$, and may never receive hence deliver a better message
  than $\alpha_X$. They need an additional mechanism to eventually
  purge $\alpha_X$ that cannot rely on the eventual purging of $P_Y$
  to avoid deadlocks.

  Assuming that every \process keeps an history of its past
  deliveries, \processes (such as $c$) can detect the inconsistency,
  since they receive from their parent an already deleted partition
  $P_Y$. This notification means that the parent discards any
  $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
  $\delta_X$ exists, it discards it. To ensure the purge of stale
  messages, a detecting \process must assume the worst case that such
  $\delta_X$ exists, and send another kind of message, noted $\Delta$
  that notify the possible removal of $P_X$. Children \processes that
  still have $P_X$ as last delivery must trust the detecting \process
  and remove the possibly stale control information about $P_X$.

@@

  % ; and since \processes forward the messages they deliver, upstream
  % \processes eventually receive and may deliver messages detected as
  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
  % receives $\delta_f$ from \Process~$b'$.
  These three phases propagation-detection-propagation ensure that
  \processes eventually purge stale $\alpha$ messages from the system,
  leaving room for best eventual forwarding of up-to-date messages.
  %
  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
  % delete to $e$, it will solve the inconsistency.}
  %
  %% In the meantime, \processes that still belong to a partition can
  %% propagate their respective last $\alpha$ message, and reach
  %% consistent partitioning.
\end{proof}

>>>>

\begin{theorem}[\label{theo:threephase}Three-phase purge]
  The following three phases are sufficient to eventually purge the
  system from stale control information:
  \begin{inparaenum}[(i)]
  \item propagation of delete notifications,
  \item detection of possibly blocking conditions, and
  \item propagation of possibly deleted but blocked notifications.
  \end{inparaenum}
\end{theorem}

@@

  These exceptions eventually receive and deliver $\alpha_Y$ since
  $\alpha_Y$ is better than $\alpha_X$ through this path, except if
  they already received and delivered the removal notification of
  $P_Y$ (such as $c$). These \processes may never receive hence
  deliver $\delta_X$, and may never receive hence deliver a better
  message than $\alpha_X$. They need an additional mechanism to
  eventually purge $\alpha_X$ that cannot rely on the eventual purging
  of $P_Y$ at \processes like $b$, to avoid deadlocks.

  Assuming that every \process keeps an history of its past
  deliveries, \processes (such as $c$) can detect the inconsistency,
  since they receive from their parent an already deleted partition
  $P_Y$. This notification means that the parent discards any
  $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
  $\delta_X$ exists, it discards it. To ensure the purge of stale
  messages, a detecting \process must assume the worst case that such
  $\delta_X$ exists, and send another kind of message, noted $\Delta$,
  that notify the possible removal of $P_X$.

  A \process (such as $d$) whose last delivery is $\alpha_X$, but
  whose parent is neither inconsistent (like $b$) nor receiving
  $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
  \process, either directly or transitively, for such a child \process
  ($d$) trusts the possible removal of $P_X$ by delivering and
  forwarding such $\Delta$. $\Delta$ suffers from identical blocking
  conditions (between $b$ and $c$) than $\delta$, leading to the same
  solutions of detection and propagation of $\Delta$. Eventually,
  every \process whose last delivery is $\alpha_X$ receives and
  delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.

@@

  % ; and since \processes forward the messages they deliver, upstream
  % \processes eventually receive and may deliver messages detected as
  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
  % receives $\delta_f$ from \Process~$b'$.
  Three-phase purge ensures that all \processes of the system
  eventually removes stale $\alpha$ messages, leaving room for best
  eventual forwarding of up-to-date messages.
  %
  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
  % delete to $e$, it will solve the inconsistency.}
  %
  %% In the meantime, \processes that still belong to a partition can
  %% propagate their respective last $\alpha$ message, and reach
  %% consistent partitioning.
\end{proof}
